Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-04 Draft/Draft.Rmd
last added edits

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 2. Comparison of the motif frequencies between empirical and simulated networks. Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks. The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=8,fig.height=5}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

2) FG-position associations.
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(lme4)
library(nlme)
library(tidyverse)
library(stringi)
library(ggpubr)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

# Plant and Pollinators--------

ggarrange(GF_plant_pos,GF_poll_pos,
          ncol = 1, nrow = 2,heights = c(.90, 1.4))

#Fig 2 may be the same, but for the each positions-FG combination? Maybe heatmap (but we lose the SE's)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8}

@@

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 2. Comparison of the motif frequencies between empirical and simulated networks. Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks. The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(lme4)
library(nlme)
library(tidyverse)
library(stringi)
library(ggpubr)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

# Plant and Pollinators--------
#
#ggarrange(GF_plant_pos,GF_poll_pos,
#          ncol = 1, nrow = 2,heights = c(.90, 1.4))
#
#Fig 2 may be the same, but for the each positions-FG combination? Maybe heatmap (but we lose the SE's)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8, fig.cap="Figure 3. . Comparison of the motif frequencies between empirical and simulated networks collapsing the networks nodes by functional plant and pollinator functional groups. Mean percentiles close to 0 and 1 indicate under- and over- representation respectively."}

@@

Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions. The different motif positions are dividied by the average path length clasification by @simmons2020
